Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-16 paper/paper.tex
Add the list of short-lived unrecognized states #54

This paper attempts to estimate the impact of being unrecognized as a sovereign state on economic activities in these four territories of the former Soviet Union. 
Although we focus only on four cases of unrecognized states, there are several other cases of unrecognized states.
Somaliland in northwest Somalia has not been recognized by any country since 1991. 
Taiwan and Northern Cyprus have been recognized only by a few countries since the 1970s. 
Since 2008, Kosovo has been recognized as independent by many countries, but not by the others including its parent country Serbia.
More recently, the 2014 crisis in Ukraine resulted in the creation of two unrecognized states in its eastern area: Luhansk and Donetsk.
It is therefore important to understand the consequences of being unrecognized as sovereign states because not an ignorable number of people now live in such pseudo states today.

>>>>

This paper attempts to estimate the impact of being unrecognized as a sovereign state on economic activities in these four territories of the former Soviet Union. 
Although we focus only on four cases of unrecognized states, there are several other cases of unrecognized states.
Somaliland in northwest Somalia has not been recognized by any country since 1991. 
Taiwan and Northern Cyprus have been recognized only by a few countries since the 1970s. 
Since 2008, Kosovo has been recognized as independent by many countries, but not by the others including its parent country Serbia.
More recently, the 2014 crisis in Ukraine resulted in the creation of two unrecognized states in its eastern area: Luhansk and Donetsk.
It is therefore important to understand the consequences of being unrecognized as sovereign states because not an ignorable number of people now live in such pseudo states today.%
\footnote{
	There were more short-lived cases of unrecognized states: Katanga in Zaire (Democratic Republic of Congo) during 1960--63, Republika Srpska Krajina in Croatia during 1991--95, Republika Srpska in Bosnia-Herzegovina during 1992--95, and Chechnya in Russia during 1996-99.
	}
